---
title: "Lab 10 - Grading the professor, Pt. 2"
author: "Insert your name here"
date: "Insert date here"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidymodels)
library(openintro)
library(openintro)
```

### Exercise 1
```{r}
evals2<-evals

rr<-linear_reg(mode="regression") %>%
  set_engine("lm")

m_bty<-rr %>%
  fit(score~bty_avg, data=evals2)
  
m_bty
summary(m_bty$fit)
```
Multiple R-squared:  0.03502,	Adjusted R-squared:  0.03293 
y=3.88+0.07bty_avg

### Exercise 2
```{R}


rr<-linear_reg(mode="regression") %>%
  set_engine("lm")

m_bty_gen<-rr %>%
  fit(score~bty_avg+factor(gender), data=evals2)
  
m_bty_gen
summary(m_bty_gen$fit)


```
Multiple R-squared:  0.05912,	Adjusted R-squared:  0.05503 
y=3.74+0.07*bty_evg + 0.17*gender
5%
male
y=3.74+0.17+0.07*bty_evg
male
being a male is beneficial to get a high score, when the beaty score is the same. 

8
adding gender variable is beneficial for get a higher R^2

9
not that much 

##ex10

```{r}




rr<-linear_reg(mode="regression") %>%
  set_engine("lm")

m_bty_rank<-rr %>%
  fit(score~bty_avg+rank, data=evals2)
  
m_bty_rank
summary(m_bty_rank$fit)


```
y = 3.98 + 0.06bty_avg -0.16 rank(tenure track) - 0.12rank(tenured)

compared to the reference group, 
being a tenure tract or tenured is detrimental to y


##ex11,12

```{r}



ci <- lm(score ~ cls_profs, data=evals2)
summary(ci)
```
p=0.58... cls_profs is not significant predictor to score.


13
cls_did eval may overlapped with other predictors. 


##ex1415

```{r}

ex14<- rr %>%
  fit(score~rank+ethnicity+gender+language+age+
        cls_perc_eval+cls_students+cls_level + cls_profs+
        cls_credits+bty_avg, data=evals2 )
summary(ex14$fit)

```

```{r}

back<-lm(score~factor(rank)+factor(ethnicity)+factor(gender)+factor(language)+age+
        cls_perc_eval+cls_students+factor(cls_level) + factor(cls_profs)+
        factor(cls_credits)+bty_avg, data=evals2 )

summary(back)

back2<-stats::step(back, direction="backward")

back2$anova

#final model 

back2$coefficients
```

being a male is beneficial to score about 0.18 to score while other things are equal. 
one unit increase in bty_avg is related in 0.06 increase in the score while other things are equal. 

typically, not being an moniroty,being male, engislh, and young, and  one credit, and good looking professors get higher scores. 

No.
Need more data from different university, region..etc. 
